\problemname{FizzBuzz}
A company is hiring a software engineer to a top secret job.
After a lot of headhunting they now have $N$ candidates left, denoted $1$ to $N$ after anonymization.
To test the skills of the candidates, the company has asked them to implement FizzBuzz.

A correct implementation of FizzBuzz does the following.
For each and every of the integers $1$ to $M$,
\begin{itemize}
  \item if the number is divisible by $3$, ``fizz'' is output,
  \item if the number is divisible by $5$, ``buzz'' is output,
  \item if the number is divisible by both $3$ and $5$, ``fizzbuzz'' is output, and
  \item if the number is divisible by neither $3$ and $5$, the number itself is output.
\end{itemize}

Since the job is top secret, the company cares very much about the right thing being printed in the right place.
Your task is to find the candidate whose program outputs the right thing at the right position the most times.

\section*{Input}
The first line of the input consists of the integers $N$ ($2 \leq N \leq 1000$) and $M$ ($2 \leq M \leq 100$), the number of candidates and the number of values their programs should output.

The next $N$ lines each contains $M$ strings consisting only of small letters \texttt{a-z} and digits $0$-$9$, separated by a single whitespace.
The $i$'th of these lines contains the output from candidate $i$.
Each of the $M$ strings in the output from a candidate contains at least one character.

\section*{Output}
Print the number of the candidate whose output has the most correct things printed in the correct place.
In case of a tie, output the candidate with the lowest number.

\section*{Explanation of sample 1}
In the example, the third candidate output the right thing at every place.
The other two has at least one incorrect output, so the third person has the most correct words.
